---
title: "CP_CILSPrep"
output:
  word_document: default
  html_document:
    df_print: paged
---

## R Markdown

Load in libraries I will be using for this project

```{r message=FALSE, warning=FALSE}

library(statnet)
library(foreign)
library(readstata13)
library(tidyr)
library(dplyr)
library(knitr)
library(sna)


```

Delete memory so that workspace is blank when running code
```{r setup}

#Deleting memory and resetting global environment
rm(list=ls())

setwd("~/University/Project/Code")
knitr::opts_knit$set(echo = TRUE)
knitr::opts_knit$set(root.dir = normalizePath("~/University/Project/Code"))
getwd()

```

## Generate the network objects for Wave 1 of the CILS4EU Germany Data

Gather classmate data for Wave 1

```{r message=FALSE, warning=FALSE}

classmates.raw <- read.dta13("youth classmates/w1_yc_ge_v1.2.0_rv.dta")

# Variables of interest - only keep the meta-data and the best friends data
vi<- c("youthid", "classid", "schoolid", "y1_nnominatorG","y1_outnomsG","y1_absnomsG", "y1_classid_matchG", "y1_bfs_1", "y1_bfs_2","y1_bfs_3", "y1_bfs_4", "y1_bfs_5")

# Limit data to classes where nobody moved and where only present students could be nominated 
valid<- (classmates.raw[,"y1_classid_matchG"] == 1 & classmates.raw[,"y1_absnomsG"] == 0 & classmates.raw[,"y1_classid_matchG"] == 1)
classmates<- classmates.raw[valid, vi]
nets<-list()

# For each classid
classids <- unique(classmates[,"classid"])


```

Loop over classmates data for Wave 1 of the CILS4EU Germany Data

```{r warning=FALSE}
i <- 1
for (cid in classids) {
class <- classmates[classmates$classid == cid, ]
  
  # These are the unique ids of all adolescents in classid = cid who answered the survey of friendship ties.
  class.youthids<- unique(class$youthid)
  class.bfs <- class[,c("youthid","y1_bfs_1", "y1_bfs_2","y1_bfs_3", "y1_bfs_4", "y1_bfs_5")]
  
  
  # This generates a clean edgelist for each network
  class.edgelist <- class.bfs %>% gather(x, alter, y1_bfs_1:y1_bfs_5)
  class.edgelist <- class.edgelist[class.edgelist$alter>0, c("youthid", "alter")]
  
  # Turn the values in the edgelist into characters.
  ego<-as.character(class.edgelist[,"youthid"])
  alter<-as.character(class.edgelist[,"alter"])
  
  # This check is needed in case the edgelist is empty
  if (length(ego)>0) {
    n<-network(cbind(ego, alter), matrix.type = "edgelist")
    n %n% "classid" <- cid
    nets[[i]]<- n
    i<-i+1
  }
}

```

## Adds Wave 1 Data from the main survey of the CILS4EU Germany Data

Extract data from main survey Germany Wave 1

```{r warning=FALSE}

main.raw <- read.dta13("youth main/w1_ym_ge_v1.2.0_rv.dta")

#Convert all values that represent missing information to NA values
main.raw[main.raw == -55] <- NA
main.raw[main.raw == -88] <- NA
main.raw[main.raw == -77] <- NA
main.raw[main.raw == -99] <- NA

```

Loop over main survey to find data for students that took part in the classmates friendship survey and main survey
```{r}

# Run through all networks
for (i in 1:length(nets)){

  # Extract youthids for one network. This will be used to match with the main survey.
  youthid <- as.numeric(nets[[i]] %v% "vertex.names")
  class.net<- as.data.frame(cbind(youthid, net=1))
  class.main <- main.raw[main.raw[,"youthid"] %in% youthid,]
  class.sorted <-merge(class.net, class.main, by="youthid", all.x = T)
  
  # Generate node level attribute for each variable in main data
  v<-names(class.sorted)
  for (j in 3:length(v)){
    if (is.factor(class.sorted[,j])) {
      # This line turns factor variables into strings.
      nets[[i]] %v% v[j] <- as.character(class.sorted[,j])
    }
    else {
      nets[[i]] %v% v[j] <- class.sorted[,j]
    }
  }
}


```

## Adds Wave 1 Data from the achievement survey of the CILS4EU Germany Data

Extract data from achievement survey Germany Wave 1
```{r warning=FALSE}

achieve.raw <- read.dta13("youth achievement_stata13/w1_ya_ge_v1.2.0_rv.dta")

```

Loop over main survey to find data for students that took part in the classmates friendship survey and achievement survey

```{r}

# Run through all networks
for (i in 1:length(nets)){
  
  # Extract youthids for one network. This will be used to match with the main survey.
  youthid <- as.numeric(nets[[i]] %v% "vertex.names")
  class.net<- as.data.frame(cbind(youthid, net=1))
  class.achieve <- achieve.raw[achieve.raw[,"youthid"] %in% youthid,]
  class.sorted <-merge(class.net, class.achieve, by="youthid", all.x = T)
  
  # Generate node level attribute for each variable in main data
  v<-names(class.sorted)
  for (j in 3:length(v)){
    if (is.factor(class.sorted[,j])) {
      # This line turns factor variables into strings.
      nets[[i]] %v% v[j] <- as.character(class.sorted[,j])
    }
    else {
      nets[[i]] %v% v[j] <- class.sorted[,j]
    }
  }
}

```


## Recoding

Recoding data to convert string to numeric values for later regression analysis

```{r}

# Let's recode gender so girl = 1 and boy = 0

for (i in 1:length(nets)){
  y1_sex <- nets[[i]] %v% "y1_sex"
  y1_sex_recoded <- ifelse(y1_sex == "girl", 1, ifelse(y1_sex == "boy", 0, NA))
  nets[[i]] %v% "y1_sex_recoded" <-  y1_sex_recoded
}

# Let's recode country of birth so no answer = NA, Germany = 1, outside Germany = 2


for (i in 1:length(nets)){
  y1_cobRV <- nets[[i]] %v% "y1_cobRV"
  y1_cobRV_recoded <- ifelse(y1_cobRV == "no answer", NA, ifelse(y1_cobRV == "survey country", 1, ifelse(y1_cobRV == "outside survey country", 2,  NA)))
  nets[[i]] %v% "y1_cobRV_recoded" <-  y1_cobRV_recoded
}


# Let's recode mother employment status so no answer = NA, Employed = 1, Unemployed = 2

for (i in 1:length(nets)){
  y1_emplm <- nets[[i]] %v% "y1_emplm"
  y1_emplm_recoded <- ifelse(y1_emplm == "no answer", NA, ifelse(y1_emplm == "dont know", NA, ifelse(y1_emplm == "question not asked", NA,
                                                                                                     ifelse(y1_emplm == "yes", 1,ifelse(y1_emplm == "no", 0,  NA)))))
  nets[[i]] %v% "y1_emplm_recoded" <-  y1_emplm_recoded
}

# Let's recode father employment status so no answer = NA, Employed = 1, Unemployed = 0

for (i in 1:length(nets)){
  y1_emplf <- nets[[i]] %v% "y1_emplf"
  y1_emplf_recoded <- ifelse(y1_emplf == "no answer", NA, ifelse(y1_emplf == "dont know", NA, ifelse(y1_emplf == "question not asked", NA, ifelse(y1_emplf == "yes", 1,
                                                                                                                                               ifelse(y1_emplf == "no", 0,  NA)))))
  nets[[i]] %v% "y1_emplf_recoded" <-  y1_emplf_recoded
}


# Let's recode third level education of mother so no answer = NA, other missing = NA, Question not asked = NA, Don't Know = NA 
# yes = 1, no = 0

for (i in 1:length(nets)){
  y1_educm3 <- nets[[i]] %v% "y1_educm3"
  y1_educm3_recoded <- ifelse(y1_educm3 == "no answer", NA, ifelse(y1_educm3 == "other missing", NA, ifelse(y1_educm3 == "question not asked", NA, ifelse(y1_educm3 == "dont know", NA,
  ifelse(y1_educm3 == "yes", 1, ifelse(y1_educm3 == "no", 0,  NA))))))
  nets[[i]] %v% "y1_educm3_recoded" <-  y1_educm3_recoded
}


# Let's recode third level education of father so no answer = NA, other missing = NA, Question not asked = NA, Don't Know = NA 
# yes = 1, no = 0

for (i in 1:length(nets)){
  y1_educf3 <- nets[[i]] %v% "y1_educf3"
  y1_educf3_recoded <- ifelse(y1_educf3 == "no answer", NA, ifelse(y1_educf3 == "other missing", NA, ifelse(y1_educf3 == "question not asked", NA, ifelse(y1_educf3 == "dont know", NA, ifelse(y1_educf3 == "yes", 1, ifelse(y1_educf3 == "no", 0,  NA))))))
  nets[[i]] %v% "y1_educf3_recoded" <-  y1_educf3_recoded
}


# Let's recode attitude education importance so no answer = NA, other missing = NA
#Strongly Agree = 5, Agree = 4, Neither agree nor disagree = 3, Disagree = 2, Strongly disagree = 1

for (i in 1:length(nets)){
  nets[[i]] %v% "y1_valed1"
  y1_valed1 <- nets[[i]] %v% "y1_valed1"
  y1_valed1_recoded <- ifelse(y1_valed1 == "no answer", NA,
                              ifelse(y1_valed1 == "other missing", NA,
                                     ifelse(y1_valed1 == "strongly agree", 5,
                                     ifelse(y1_valed1 == "agree", 4,
                                     ifelse(y1_valed1 == "neither agree nor disagree", 3,
                                            ifelse(y1_valed1 == "disagree", 2,
                                                   ifelse(y1_valed1 == "strongly disagree", 1, NA)))))))
  nets[[i]] %v% "y1_valed1_recoded" <- y1_valed1_recoded
}


# Let's recode second language spoken at home. no answer = NA, Yes = 1, No = 0

for (i in 1:length(nets)){
  y1_loc1 <- nets[[i]] %v% "y1_loc1"
  y1_loc1_recoded <- ifelse(y1_loc1 == "no answer", NA, ifelse(y1_loc1 == "yes", 1, ifelse(y1_loc1 == "no", 0,  NA)))
  nets[[i]] %v% "y1_loc1_recoded" <-  y1_loc1_recoded
}

```

Saving created network data

```{r}

#Setting new working directory to save network data and attributes saved as network

setwd("~/University/Project/R")
knitr::opts_knit$set(echo = TRUE)
knitr::opts_knit$set(root.dir = normalizePath("~/University/Project/Code"))
setwd("~/University/Project/R")
save(nets, file="cils_ge_nets.Rdata")
rm(list=ls())

#Load saved network data

load(file="cils_ge_nets.Rdata")


```

## Collating data to dataframe

Function that calculates degree where only nodes with certain attributes are considered. 

```{r}

#Function that calculates degree where only certain attributes are considered

degree_attr<- function(net, attr, value,...){
  v.attr<-get.vertex.attribute(net, attr)
  adj.matrix<-as.matrix(net)
  sna::degree
network::get.vertex.attribute
  v.adj.matrix <- adj.matrix * t(matrix(rep((v.attr == value), network.size(net)), nrow=network.size(net)))
  degree(v.adj.matrix,...)
}

```

Creating empty Master Data Frame and looping attributes to be added from networks into data frame structure

```{r}
master_df <- data.frame()

for (i in 1:length(nets)){
  youthid<- nets[[i]] %v% "vertex.names"
  gender <- nets[[i]] %v% "y1_sex_recoded"
  country_birth <- nets[[i]] %v% "y1_cobRV_recoded"
  maths_score <- nets[[i]] %v% "y1_gradem_ge"
  language_score <- nets[[i]] %v% "y1_lat_sum"
  eng_score <- nets[[i]] %v% "y1_gradee_ge"
  ger_score <- nets[[i]] %v% "y1_gradesc_ge"
  cognitive_score <- nets[[i]] %v% "y1_cot_sum"
  maths_score_rev <- nets[[i]] %v% "maths_score_rev" <- 7 - maths_score
  ger_score_rev<- nets[[i]] %v% "ger_score_rev" <- 7 - ger_score
  eng_score_rev <- nets[[i]] %v% "eng_score_rev" <- 7 - eng_score
  cognitive_rec <- nets[[i]] %v% "cognitive_rec" <- cognitive_score/6
  lang_rec <- nets[[i]] %v% "lang_rec" <- language_score/6
  country_birth <- nets[[i]] %v% "country_birth" <- country_birth
  mother_employ <- nets[[i]] %v% "y1_emplm_recoded"
  father_employ <- nets[[i]] %v% "y1_emplf_recoded"
  mother_educate3 <- nets[[i]] %v% "y1_educm3_recoded"
  father_educate3 <- nets[[i]] %v% "y1_educf3_recoded"
  school_attitude <- nets[[i]] %v% "y1_sat2" #1 is very unsatisfied and 10 is very satisfied with school
  lang_2 <- nets[[i]] %v% "y1_loc1_recoded"
  value_education <- nets[[i]] %v% "y1_valed1_recoded"
  number_of_native_friends <- degree_attr(nets[[i]], attr="y1_cobRV", value="survey country", cmode="outdegree")
  number_of_migrant_friends <- degree_attr(nets[[i]], attr="y1_cobRV", value="outside survey country", cmode="outdegree")
  outdeg<-degree(nets[[i]],cmode="outdegree")
  df<- data.frame(youthid=as.numeric(youthid), gender, country_birth, maths_score_rev=as.numeric(maths_score_rev), lang_rec=as.numeric(lang_rec),
             eng_score_rev=as.numeric(eng_score_rev), ger_score_rev=as.numeric(ger_score_rev), cognitive_rec=as.numeric(cognitive_rec),
             mother_employ, father_employ, outdeg, number_of_native_friends = as.numeric(number_of_native_friends),
             number_of_migrant_friends=as.numeric(number_of_migrant_friends), mother_employ, mother_educate3, father_employ,
             father_educate3, lang_2, school_attitude=as.numeric(school_attitude), value_education)
  master_df <- rbind(master_df, df)
}



```


Checking dataframe was created successfully
```{r include=FALSE}

#Checking dimensions of dataframe to see if it loaded correctly
dim(master_df)

#Loading tidyr to run the dropna function on dataframe
library(tidyr)
master_df %>% drop_na()


```

Adding more data to dataframe

```{r}

#Creating column with share of migrant friends
master_df$share_mig <- master_df$number_of_migrant_friends / (master_df$number_of_migrant_friends + master_df$number_of_native_friends)


#Creating column with total number of friends
master_df$number_of_friends<- master_df$number_of_migrant_friends + master_df$number_of_native_friends

```


## Analysing Data


Statistics on data

```{r}
#How many students in our survey?

nrow(master_df) #1517 students

#How many classes in our analysis?

length(nets) #93 classrooms/networks

#How many male and female in our network?

table(master_df$gender) #741 Females, 774 Males

#How many migrants in network?

table(master_df$country_birth) #1334 Natives, 173 Migrants
```

Creating Summary Statistics Table

```{r}

#Loading stargazer library to create tables
library(stargazer)

#Applying mean function and saving to a new dataframe.
#Calculates mean of columns in master_df dataframe
Summ_DF<-sapply(master_df,FUN=mean, na.rm = T)

#Calculates median of columns in master_df dataframe and saves to new variable
Med<-sapply(master_df,FUN=median, na.rm = T)

#Calculates standard deviation of cola in master_df and save to new variable
Standard_Dev<-sapply(master_df,FUN=sd, na.rm = T)

#Calculates minimum of columns in master_df dataframe and saves to new variable
Minm <- sapply(master_df,FUN=min, na.rm = T)

#Calculates maximum of columns in master_df dataframe and saves to new variable
Maxm <- sapply(master_df,FUN=max, na.rm = T)

#Calculates inter quartile range of cols in master_df and saves to new variable
InQuar <- sapply(master_df,FUN=IQR, na.rm = T)

#Adding all the summary statistics gathered and saving to one dataframe
Summ_DF <- cbind(Summ_DF, Med, Standard_Dev, Minm, Maxm, InQuar)


#Creating function that will round all the values down in our dataframe
round_df <- function(x, digits) {
    # round all numeric variables
    # x: data frame 
    # digits: number of digits to round
    numeric_columns <- sapply(x, mode) == 'numeric'
    x[numeric_columns] <-  round(x[numeric_columns], digits)
    x
}

#Applying rounding function and saving to new dataframe Summ_DF2
Summ_DF2 <- round_df(Summ_DF, 2)

#Creating new dataframe with new row and col names and some ordinal values drop
Summary_Dat <- Summ_DF2[-c(1, 2, 3, 9, 10, 14, 15, 16, 17, 18), ] 
colnames(Summary_Dat) <- c("Mean","Median","Standard Deviation","Minimum","Maximum","IQR")
rownames(Summary_Dat)<- c("Maths Score","Language Score","English Score","German Score","Cognitive Score",
                          "Outdegree", "Native Friends", "Migrant Friends","Attitude to School","Value of Education",
                          "Share of Migrant Friends", "Total Friends")

#Creating summary statistics table to add to dissertation
stargazer(Summary_Dat,header=F,type ='html',title ="Summary Statistics",out ="Summ_Stats")

```

Network Stats
```{r}

#Loading sna library to conduct social network analysis
library(sna)

#NETWORK LEVEL STATS

#Calculate Network Density of our networks

Network_Density <- gden(nets) #Network density levels. 0 = Nobody is connected.

#Creating Network Density scatter plot
par(mfrow=c(1,2))
plot(Network_Density, ylab = "Network Density", main = "Network Density Plot",
     pch = 19, col = "blue")
abline(h=mean(Network_Density), col="red") #Add red line where the mean is on plot
legend("topright", c("Mean of Network Density"), #Add a legend
       col = c("red"), lty = c(1), lwd = c(1),
       xpd=TRUE, inset=c(0,0), cex=0.55, bty='n')
mean(Network_Density) #Checking mean value of network density


#Calculating Network Transitivity of our networks

Network_Transitivity <- gtrans(nets) #Transitivity scores. Network level measure for each network 1 is all triads, 0 no triads

#Network Transitivity scatter plot
plot(Network_Transitivity, ylab = "Network Transitivity", main = "Network Transitivity Plot",
     pch = 19, col = "blue")
abline(h=mean(Network_Transitivity), col="red") #Add red line where the mean is on plot
legend("topright", c("Mean of Network Transitivity"), #Add a legend
       col = c("red"), lty = c(1), lwd = c(1),
       xpd=TRUE, inset=c(0,0), cex=0.55, bty='n')
mean(Network_Transitivity) #Checking mean value of network transitivity

#NODE LEVEL STATS
par(mfrow=c(1,1))

#Calculate degree centrality of nodes in our networks
Network_Degree_Central <- sna::degree(nets,cmode="outdegree")

#Creating histogram of Network Degree Centrality scores
hist(Network_Degree_Central, main = "Network Degree Centrality Score",
     xlab="Node Degree Centrality Scores",  breaks=seq(0,6.5,1),  col = "light blue")
abline(v=mean(Network_Degree_Central), col="red") #Add red line where the mean is on plot
legend("topright", c("Mean Degree Centrality"), #Add a legend
       col = c("red"), lty = c(1), lwd = c(1),
       xpd=TRUE, inset=c(0,0), cex=0.55, bty='n')
mean(Network_Degree_Central) #Checking mean value of degree centrality

```


Histogram of the students last maths, german and english grades in school
Histogram of the tests of language and cognitive ability conducted by CILS4EU team

```{r}

par(mfrow=c(1,2))
hist(master_df$maths_score_rev, main = "Maths Score",
     xlab="Grade", ylab="Maths Score",  breaks=seq(0.5,6.5,1), col = "light blue")

hist(master_df$ger_score_rev, main = "German School Score",
     xlab="Grade", ylab="German Score",  breaks=seq(0.5,6.5,1), col = "light blue")

hist(master_df$eng_score_rev, main = "English School Score",
     xlab="Grade", ylab="English Score",  breaks=seq(0.5,6.5,1), col = "light blue")

hist(master_df$lang_rec, main = "CILS4EU Language Score",
     xlab="Grade", ylab="No. Students", breaks=seq(0,6.5,1), col = "light blue")

par(mfrow=c(1,1))
hist(master_df$cognitive_rec, main = "CILS4EU Cognitive Score",
     xlab="Grade", ylab="No. Students", breaks=seq(0,6.5,1), col = "light blue")

```


Barplot of how many migrants there are compared to natives in study

```{r}

barplot(table(master_df$country_birth), names.arg=c("German","Migrant"), col = "light blue", ylim=c(0,1400))
title("Number of Native Germans and Migrants")

```


```{r}

barplot(table(master_df$gender), names.arg=c("Female", "Male"), col = "light blue", ylim=c(0,800))
title("Number Female and Male Students")

```


Barplot of how many migrant students have a second language

```{r}

barplot(table(master_df$lang_2), names.arg=c("No 2nd Language", "2nd Language"), col = "light blue", ylim=c(0,1000))
title("Second Language of Migrants")

```

Histograms of share migrant friends and share of migrants in the schools

```{r}

hist(master_df$share_mig, main = "Share Migrant Friends",
     xlab="Percentage Share Migrant Friends", ylab="Number Students", breaks=seq(0,1,0.2), col = "light blue")


```

Barplots of employment status of parents

```{r}
par(mfrow=c(1,2))

barplot(table(master_df$mother_employ), names.arg=c("Unemployed","Employed"), col = "light blue", ylim=c(0,1200))
title("Mother Employment")

barplot(table(master_df$father_employ), names.arg=c("Unemployed","Employed"), col = "light blue", ylim=c(0,1200))
title("Father Employment")

```

Barplots of level 3rd Level Education of parents

```{r}

par(mfrow=c(1,2))

barplot(table(master_df$mother_educate3), names.arg=c("No 3rd Level", "3rd Level"), col = "light blue", ylim=c(0,1200))
title("Mother 3rd Level Education")

barplot(table(master_df$father_educate3), names.arg=c("No 3rd Level", "3rd Level"), col = "light blue", ylim=c(0,1200))
title("Father 3rd Level Education")


```

Histograms on attitude of students to education and their perceived value of education

```{r}

par(mfrow=c(1,2))

hist(master_df$value_education, main = "Value of Education Attitude",
     xlab="How Important is Education", ylab="Number Students",breaks=seq(0,5,1),col = "light blue", ylim=c(0,1200))

hist(master_df$school_attitude, main = "Attitude Towards School",
     xlab="Attitudes Towards School", ylab="Number Students", breaks=seq(0,10,1), col = "light blue",  ylim=c(0,350))


```

## Regressions

First I will run regressions studying natives only against share migrant friends

```{r}

#Maths score regressed against share migrant friends, gender and total number of friends
m1<-lm(maths_score_rev~share_mig + gender + number_of_friends + father_employ + mother_employ + father_educate3 + mother_educate3 + school_attitude + value_education, data=master_df[master_df$country_birth=="1",])
summary(m1)

#German score regressed against share migrant friends, gender and total number of friends
m2<-lm(ger_score_rev~share_mig + gender + number_of_friends + father_employ + mother_employ + father_educate3 + mother_educate3 + school_attitude + value_education, data=master_df[master_df$country_birth=="1",])
summary(m2)

#English score regressed against share migrant friends, gender and total number of friends
m3<-lm(eng_score_rev~share_mig + gender + number_of_friends + father_employ + mother_employ + father_educate3 + mother_educate3 + school_attitude + value_education, data=master_df[master_df$country_birth=="1",])
summary(m3)

#Language score regressed against share migrant friends, gender and total number of friends
m4<-lm(lang_rec~share_mig + gender + number_of_friends + father_employ + mother_employ + father_educate3 + mother_educate3 + school_attitude + value_education, data=master_df[master_df$country_birth=="1",])
summary(m4)

#Cognitive score regressed against share migrant friends, gender and total number of friends
m5<-lm(cognitive_rec~share_mig + gender + number_of_friends + father_employ + mother_employ + father_educate3 + mother_educate3 + school_attitude + value_education, data=master_df[master_df$country_birth=="1",])
summary(m5)


```

Running regressions for migrants only against share migrant friends

```{r}

#Maths score regressed against share native friends, gender and total number of friends
m01<-lm(maths_score_rev~share_mig + gender + number_of_friends + father_employ + mother_employ + father_educate3 + mother_educate3 + school_attitude + value_education + lang_2, data=master_df[master_df$country_birth=="2",])
summary(m01)

#German score regressed against share native friends, gender and total number of friends
m02<-lm(ger_score_rev~share_mig + gender + number_of_friends + father_employ + mother_employ + father_educate3 + mother_educate3 + school_attitude + value_education + lang_2, data=master_df[master_df$country_birth=="2",])
summary(m02)

#English score regressed against share native friends, gender and total number of friends
m03<-lm(eng_score_rev~share_mig + gender + number_of_friends + father_employ + mother_employ + father_educate3 + mother_educate3 + school_attitude + value_education + lang_2, data=master_df[master_df$country_birth=="2",])
summary(m03)

#Language score regressed against share native friends, gender and total number of friends
m04<-lm(lang_rec~share_mig + gender + number_of_friends + father_employ + mother_employ + father_educate3 + mother_educate3 + school_attitude + value_education + lang_2, data=master_df[master_df$country_birth=="2",])
summary(m04)

#Cognitive score regressed against share native friends, gender and total number of friends
m05<-lm(cognitive_rec~share_mig + gender + number_of_friends + father_employ + mother_employ + father_educate3 + mother_educate3 + school_attitude + value_education + lang_2, data=master_df[master_df$country_birth=="2",])
summary(m05)

```

Running regression analysis on the five native models to test assumptions of linear regression models

```{r}

par(mfrow=c(1,2))
plot(m1)
plot(m2)
plot(m3)
plot(m4)
plot(m5)

```

Running regression analysis on the six migrant models to test assumptions of linear regression models

```{r}

par(mfrow=c(1,2))
plot(m01)
plot(m02)
plot(m03)
plot(m04)
plot(m05)

```



## Network Plots

```{r}

#Plotting network number 13 with node size corresponding to academic score

#Red plots are Migrant Students. Black plots are Native Students

#MATHS SCORE NETWORK

par(mfrow=c(1,2))
set.seed(123) #Setting seed so all network plots run will look the same
plot(nets[[13]], vertex.cex = "maths_score_rev", vertex.col = "country_birth", displaylabels=F, title = "Maths Score Network")
legend("bottomleft", inset=.02,
       c("Migrant","Native"), fill=c("red","black"), horiz=TRUE, cex=0.8)
title(main = "Maths Score Network")

#GERMAN SCORE NETWORK

set.seed(123) #Setting seed so all network plots run will look the same
plot(nets[[13]], vertex.cex = "ger_score_rev", vertex.col = "country_birth", displaylabels=F)
legend("bottomleft", inset=.02,
       c("Migrant","Native"), fill=c("red","black"), horiz=TRUE, cex=0.8)
title(main = "German Score Network")

#ENGLISH SCORE NETWORK

set.seed(123)#Setting seed so all network plots run will look the same
plot(nets[[13]], vertex.cex = "eng_score_rev", vertex.col = "country_birth", displaylabels=F)
legend("bottomleft", inset=.02,
       c("Migrant","Native"), fill=c("red","black"), horiz=TRUE, cex=0.8)
title(main = "English Score Network")

#LANGUAGE SCORE NETWORK

set.seed(123)#Setting seed so all network plots run will look the same
plot(nets[[13]], vertex.cex = "lang_rec", vertex.col = "country_birth", displaylabels=F)
legend("bottomleft", inset=.02,
       c("Migrant","Native"), fill=c("red","black"), horiz=TRUE, cex=0.8)
title(main = "Language Score Network")

#COGNITIVE SCORE NETWORK

set.seed(123)#Setting seed so all network plots run will look the same
plot(nets[[13]], vertex.cex = "cognitive_rec", vertex.col = "country_birth", displaylabels=F)
legend("bottomleft", inset=.02,
       c("Migrant","Native"), fill=c("red","black"), horiz=TRUE, cex=0.8)
title(main = "Cognitive Score Network")

```

## Regression Tables

Regression Table of the Native Student Models

```{r include=FALSE}

stargazer(m1,m2,m3,m4,m5,header=F,type ='html',title ="Native Academic Scores Against Share Migrant Friends",out ="Nat_Models")

```
Regression Table of the Migrant Student Models

```{r echo=TRUE}

stargazer(m01,m02,m03,m04,m05,header=F,type ='html',title ="Migrant Academic Scores Against Share Migrant Friends",out ="Mig_Models")

```
